---
title: "Convergent evolution of conserved mitochondrial pathways underlies repeated adaptation to extreme environments"
output:
  html_document:
    keep_md: TRUE
    toc: yes
    toc_depth: '3'
  pdf_document:
    toc: yes
    toc_depth: '3'
  html_notebook:
    fig_caption: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
---

# 1. Required packages and functions
```{r message=FALSE}
library(AICcmodavg)
library(bbmle)
library(car)
library(effects)
library(ggplot2)
library(heplots)
library(labdsv)
library(lme4)
library(loop)
library(MASS)
library(MuMIn)
library(nlme)
library(nplr)
library(plyr)
library(pscl)
library(sjPlot)
library(stats)
library(stats4)
library(vegan)
source("http://peterhaschke.com/Code/multiplot.R")
st.err <- function(x) {sd(x)/sqrt(length(x))}
```

# 2. Analysis of COX activity
## 2.1. Loading data
```{r warning=FALSE}
cox.data <- read.csv("cox_data_final.csv")
```

## 2.2. Model selection
```{r warning=FALSE}
#Defining alternative models
cox.null <- lmer(RelativeSlope ~ (1|ID), data=cox.data)
cox.m1 <- lmer(RelativeSlope ~ Habitat + (1|ID), data=cox.data)
cox.m2 <- lmer(RelativeSlope ~ Drainage + (1|ID), data=cox.data)
cox.m3 <- lmer(RelativeSlope ~ H2S + (1|ID), data=cox.data)
cox.m4 <- lmer(RelativeSlope ~ Habitat + Drainage + (1|ID), data=cox.data)
cox.m5 <- lmer(RelativeSlope ~ Habitat + H2S + (1|ID), data=cox.data)
cox.m6 <- lmer(RelativeSlope ~ Drainage + H2S + (1|ID), data=cox.data)
cox.m7 <- lmer(RelativeSlope ~ Habitat * Drainage + (1|ID), data=cox.data)
cox.m8 <- lmer(RelativeSlope ~ Habitat * H2S + (1|ID), data=cox.data)
cox.m9 <- lmer(RelativeSlope ~ Drainage * H2S + (1|ID), data=cox.data)
cox.m10 <- lmer(RelativeSlope ~ Habitat + Drainage + H2S + (1|ID), data=cox.data)
cox.m11 <- lmer(RelativeSlope ~ Habitat * Drainage * H2S + (1|ID), data=cox.data)

#Comparing alternative models
AICctab(cox.null,cox.m1,cox.m2,cox.m3,cox.m4,cox.m5,cox.m6,cox.m7,cox.m8,cox.m9,cox.m10,cox.m11, base =T, weights = T)
```
Model 8 is the only model with dAICc < 2.

## 2.3. Assessment of best model (cox.m8)
```{r warning=FALSE}
summary(cox.m8)
tab_model(cox.m8, digits = 4, show.df = TRUE)
```

## 2.4. Data visualization
```{r warning=FALSE}
#Calculation of descriptive statistics
cox.means <- aggregate(x=cox.data$RelativeSlope,
                   by=list(cox.data$Population, cox.data$H2S),
                   FUN=mean)
cox.se <- aggregate(x=cox.data$RelativeSlope,
                by=list(cox.data$Population, cox.data$H2S),
                FUN=st.err)

cox.means <- cbind(cox.means, cox.se$x)
names(cox.means) <- c("Population", "H2S", "Activity", "SE")

cox.means$drainage<-ifelse(cox.means$Population=="Banos","Pich",
                       ifelse(cox.means$Population=="Rosita","Pich",
                              ifelse(cox.means$Population=="Bonita","Tac",
                                     ifelse(cox.means$Population=="PSO","Tac","Puy"
                                     ))))

cox.means$Habitat<-ifelse(cox.means$Population=="Banos","S",
                      ifelse(cox.means$Population=="PSO","S",
                             ifelse(cox.means$Population=="Lluvia","S","NS"
                             )))

#Visualization
ggplot(aes(x=H2S, y=Activity, group=Population, color=Habitat, shape=drainage), data=cox.means) + 
  geom_point(size=4) +  
  geom_line(size=1) + 
  theme_classic() +
  geom_pointrange(aes(ymin=Activity-SE, ymax=Activity+SE), position=position_dodge(0.0005)) +
  scale_color_manual(values=c('#5DA5DA', '#DECF3F','#5DA5DA','#5DA5DA', '#DECF3F', '#DECF3F')) +
  geom_hline(yintercept=1, linetype="dashed") + 
  theme(legend.position = "none")
```

# 3. Analysis of SQR activity
## 3.1. Loading data
```{r}
sqr.data <- read.csv("SQRactivity.csv")
```

## 3.2. Model selection
```{r message=FALSE}
#Defining alternative models
sqr.null <- lmer(-Slope ~ (1|ID), data=sqr.data)
sqr.m1 <- lmer(-Slope ~ Habitat + (1|ID), data=sqr.data)
sqr.m2 <- lmer(-Slope ~ Drainage + (1|ID), data=sqr.data)
sqr.m3 <- lmer(-Slope ~ H2S + (1|ID), data=sqr.data)
sqr.m4 <- lmer(-Slope ~ Habitat + Drainage + (1|ID), data=sqr.data)
sqr.m5 <- lmer(-Slope ~ Habitat + H2S + (1|ID), data=sqr.data)
sqr.m6 <- lmer(-Slope ~ Drainage + H2S + (1|ID), data=sqr.data)
sqr.m7 <- lmer(-Slope ~ Habitat * Drainage + (1|ID), data=sqr.data)
sqr.m8 <- lmer(-Slope ~ Habitat * H2S + (1|ID), data=sqr.data)
sqr.m9 <- lmer(-Slope ~ Drainage * H2S + (1|ID), data=sqr.data)
sqr.m10 <- lmer(-Slope ~ Habitat + Drainage + H2S + (1|ID), data=sqr.data)
sqr.m11 <- lmer(-Slope ~ Habitat * Drainage * H2S + (1|ID), data=sqr.data)

#Comparing alternative models
AICctab(sqr.null,sqr.m1,sqr.m2,sqr.m3,sqr.m4,sqr.m5,sqr.m6,sqr.m7,sqr.m8,sqr.m9,sqr.m10,sqr.m11, base =T, weights = T)
```

Model 8 is the only model with dAICc < 2.

## 3.3. Assessment of best model (sqr.m8)
```{r warning=FALSE}
summary(sqr.m8)
tab_model(sqr.m8, digits = 4, show.df = TRUE)
```

## 3.4. Data visualization
```{r warning=FALSE}
#Calculation of descriptive statistics
sqr.means <- aggregate(x=sqr.data$Slope,
                   by=list(sqr.data$Population, sqr.data$H2S),
                   FUN=mean)
sqr.se <- aggregate(x=sqr.data$Slope,
                by=list(sqr.data$Population, sqr.data$H2S),
                FUN=st.err)

sqr.means <- cbind(sqr.means, sqr.se$x)
names(sqr.means) <- c("Population", "H2S", "Activity", "SE")

sqr.means$drainage<-ifelse(sqr.means$Population=="Banos","Pich",
                    ifelse(sqr.means$Population=="Rosita","Pich",
                           ifelse(sqr.means$Population=="Bonita","Tac",
                                  ifelse(sqr.means$Population=="PSO","Tac","Puy"
                                  ))))

sqr.means$Habitat<-ifelse(sqr.means$Population=="Banos","S",
                       ifelse(sqr.means$Population=="PSO","S",
                              ifelse(sqr.means$Population=="Lluvia","S","NS"
                                     )))
#Visualization
ggplot(aes(x=H2S, y=-Activity, group=Population, color=Habitat, shape=drainage), data=sqr.means) + 
  geom_point(size=4) +
  geom_line(size=1) +
  theme_classic() +
  geom_pointrange(aes(ymin=-Activity-SE, ymax=-Activity+SE), position=position_dodge(0.0005)) +
    scale_color_manual(values=c('#5DA5DA', '#DECF3F','#5DA5DA','#5DA5DA', '#DECF3F', '#DECF3F')) +
  geom_hline(yintercept=0, linetype="dashed") +
  ylim(-0.01,0.02) +
  theme(legend.position = "none")
```

# 4. Analysis of mitochondrial H2S concentrations in vivo
## 4.1. Loading data
```{r warning=FALSE}
mitoA.data <- read.csv("mitoA_data.csv")

#Designating variables
id <- as.factor(mitoA.data$ID)
pop <- as.factor(mitoA.data$Pop)
habitat <- as.factor(mitoA.data$Habitat)
drainage <- as.factor(mitoA.data$Drainage)
tissue <- as.factor(mitoA.data$Tissue)
bin <- mitoA.data$Bin
group <-as.factor(mitoA.data$Group)
H2S <- mitoA.data$H2Szero
mass <- mitoA.data$Mass
mito <- mitoA.data$relative.mitoA
```

## 4.2. Model selection
```{r warning=FALSE}
#Defining alternative models
mitoA.null <- lmer(mito ~ (1|id) + (1|tissue), data=mitoA.data)
mitoA.m1 <- lmer(mito ~ bin + (1|id) + (1|tissue), data=mitoA.data)
mitoA.m2 <- lmer(mito ~ habitat + (1|id) + (1|tissue), data=mitoA.data)
mitoA.m3 <- lmer(mito ~ drainage + (1|id) + (1|tissue), data=mitoA.data)
mitoA.m4 <- lmer (mito ~ bin + habitat + (1|id) + (1|tissue), data=mitoA.data)
mitoA.m5 <- lmer (mito ~ bin + drainage + (1|id) + (1|tissue), data=mitoA.data)
mitoA.m6 <- lmer (mito ~ habitat + drainage + (1|id) + (1|tissue), data=mitoA.data)
mitoA.m7 <- lmer (mito ~ bin*habitat + (1|id) + (1|tissue), data=mitoA.data)
mitoA.m8 <- lmer (mito ~ bin*drainage + (1|id) + (1|tissue), data=mitoA.data)
mitoA.m9 <- lmer (mito ~ habitat*drainage + (1|id) + (1|tissue), data=mitoA.data)
mitoA.m10 <- lmer (mito ~ bin + habitat + drainage + (1|id) + (1|tissue), data=mitoA.data)
mitoA.m11 <- lmer (mito ~ bin*habitat*drainage + (1|id) + (1|tissue), data=mitoA.data)

#Comparing alternative models
AICctab(mitoA.null,mitoA.m1,mitoA.m2,mitoA.m3,mitoA.m4,mitoA.m5,mitoA.m6,mitoA.m7,mitoA.m8, mitoA.m9,mitoA.m10,mitoA.m11, base =T, weights = T)
```

Model 4 is the only model with dAICc < 2.

## 4.3. Assessment of best model (mitoA.m4)
```{r warning=FALSE}
summary(mitoA.m4)
tab_model(mitoA.m4, digits = 4, show.df = TRUE)
```

## 4.4. Data visualization
```{r warning=FALSE}
#Calculation of descriptive statistics
mitoA.means <- aggregate(x=mitoA.data$relative.mitoA,
                   by=list(mitoA.data$Tissue,mitoA.data$Bin, mitoA.data$Group),
                   FUN=mean)
mitoA.se <- aggregate(x=mitoA.data$relative.mitoA,
                   by=list(mitoA.data$Tissue,mitoA.data$Bin, mitoA.data$Group),
                   FUN=st.err)

mitoA.means <- cbind(mitoA.means, mitoA.se$x)


names(mitoA.means) <- c("Tissue", "Bin", "Group", "mitoA", "SE")

mitoA.means$drainage<-ifelse(mitoA.means$Group=="1","Puy",
                       ifelse(mitoA.means$Group=="2","Puy",
                              ifelse(mitoA.means$Group=="3","Tac", "Tac"
                                     )))

mitoA.means$Habitat<-ifelse(mitoA.means$Group=="1","NS",
                      ifelse(mitoA.means$Group=="2","S",
                             ifelse(mitoA.means$Group=="3","NS","S"
                             )))



mitoA.means.gill <- mitoA.means[ which(mitoA.means$Tissue=="0"), ]
mitoA.means.liver <- mitoA.means[ which(mitoA.means$Tissue=="1"), ]
mitoA.means.muscle <- mitoA.means[ which(mitoA.means$Tissue=="2"), ]
mitoA.means.brain <- mitoA.means[ which(mitoA.means$Tissue=="3"), ]

p.gill <- ggplot(data=mitoA.means.gill, aes(x=Bin, y=mitoA, group=Group, color=Habitat, shape=drainage)) +
  geom_line(size=1) + 
  geom_point(size=4) + 
  theme_classic() +
  geom_pointrange(aes(ymin=mitoA-SE, ymax=mitoA+SE), position=position_dodge(0.0005)) +
  scale_color_manual(values=c('#5DA5DA','#DECF3F', '#5DA5DA','#DECF3F')) + 
  theme(legend.position = "none") + 
  scale_shape_manual(values=c(17, 15)) +
  geom_hline(yintercept=1, linetype="dashed") +
  ggtitle("Gills") +
  ylim(0,3)

p.liver <- ggplot(data=mitoA.means.liver, aes(x=Bin, y=mitoA, group=Group, color=Habitat, shape=drainage)) + 
  geom_line(size=1) + 
  geom_point(size=4) + 
  theme_classic() +
  geom_pointrange(aes(ymin=mitoA-SE, ymax=mitoA+SE), position=position_dodge(0.0005)) +
  scale_color_manual(values=c('#5DA5DA','#DECF3F', '#5DA5DA','#DECF3F')) + 
  theme(legend.position = "none") + 
  scale_shape_manual(values=c(17, 15)) +
  geom_hline(yintercept=1, linetype="dashed") + 
  ggtitle("Liver") +
  ylim(0,3)

p.muscle <- ggplot(data=mitoA.means.muscle, aes(x=Bin, y=mitoA, group=Group, color=Habitat, shape=drainage)) + 
  geom_line(size=1) + 
  geom_point(size=4) + 
  theme_classic() +
  geom_pointrange(aes(ymin=mitoA-SE, ymax=mitoA+SE), position=position_dodge(0.0005)) +
  scale_color_manual(values=c('#5DA5DA','#DECF3F', '#5DA5DA','#DECF3F')) + 
  theme(legend.position = "none") + 
  scale_shape_manual(values=c(17, 15)) +
  geom_hline(yintercept=1, linetype="dashed") + 
  ggtitle("Muscle") +
  ylim(0,3)

p.brain <- ggplot(data=mitoA.means.brain, aes(x=Bin, y=mitoA, group=Group, color=Habitat, shape=drainage)) + 
  geom_line(size=1) + 
  geom_point(size=4) + 
  theme_classic() +
  geom_pointrange(aes(ymin=mitoA-SE, ymax=mitoA+SE), position=position_dodge(0.0005)) +
  scale_color_manual(values=c('#5DA5DA','#DECF3F', '#5DA5DA','#DECF3F')) + 
  theme(legend.position = "none") + 
  scale_shape_manual(values=c(17, 15)) +
  geom_hline(yintercept=1, linetype="dashed") + 
  ggtitle("Brain") +
  ylim(0,3)

multiplot(p.gill,p.liver,p.muscle,p.brain, cols=2)
```

# 5. Analysis of mitochondrial function
## 5.1. Loading data
```{r}
resp.data <- data<-read.csv("mitochondrialrespiration.csv", header=T)
```

## 5.2. Basal respiration
### 5.2.1. Drug response analysis
```{r warning=FALSE}
#Drug response analysis
Listbasal <- split(data, data$Biological.replicate.number)
resultsbasal <- data.frame(matrix(ncol = 4, nrow = 0))

for (y in names(Listbasal)) {
  if (sum(is.na(Listbasal[[y]]$Basal)) == length(Listbasal[[y]]$Basal)) {
    cat(y) 
    cat("Is missing all data")
    resultsbasal <- rbind(resultsbasal,c("NA", "NA", "NA", "NA"))
  } else {
    model<- nplr(x=Listbasal[[y]]$Concentration, y=Listbasal[[y]]$Basal, useLog=FALSE, npars = 5)
    ID <- Listbasal[[y]]$Biological.replicate.number
    I <- model@inflPoint$x
    bA <- model@pars$bottom
    tA <- model@pars$top
    AUC <- model@AUC$Simpson
    resultsbasal <- rbind(resultsbasal,c(ID, I, bA, tA, AUC))
  }
}

#Retaining key results
resultsbasal <-  resultsbasal[c(8:12)]

#Change column names
x <- c("Biological.replicate.number", "I", "bA", "tA", "AUC")
colnames(resultsbasal) = x

#Isolate and append independent variables
idv <- data[c(1:3,5)]
idv <-idv[!duplicated(idv), ]

resultsbasal2 <- merge (idv, resultsbasal, by=c("Biological.replicate.number"))
resultsbasal2$AUC <- as.numeric(resultsbasal2$AUC)

```

### 5.2.2. Model selection
```{r}
#Defining alternative models
basal.null <- lm(AUC ~ 1, data=resultsbasal2)
basal.fit.1 <- lm(AUC ~ 1 + Drainage, data=resultsbasal2)
basal.fit.2 <- lm(AUC ~ 1 + Population, data=resultsbasal2)
basal.fit.3 <- lm(AUC ~ 1 + Drainage+Population, data=resultsbasal2)
basal.fit.4 <- lm(AUC ~ 1 + Drainage*Population, data=resultsbasal2)

#Comparing alternative models
AICctab(basal.null, basal.fit.1, basal.fit.2, basal.fit.3, basal.fit.4, base =T, weights = T)
```

The null model appears within dAICc <2. 

### 5.2.3. Visualization
```{r}
p2 <- ggplot(resultsbasal2, aes(x=Drainage, y=AUC, fill=Population)) + 
      geom_boxplot() + 
      theme_classic() +
      scale_fill_manual(values=c("#5DA5DA", "#DECF3F")) + 
      theme(legend.position="none") +
      ggtitle("Mitochondrial function")
p2
```

## 5.3. Maximal respiration
### 5.3.1. Drug response analysis
```{r warning=FALSE}
Listmax <- split(data, data$Biological.replicate.number)
resultsmax <- data.frame(matrix(ncol = 4, nrow = 0))

for (y in names(Listmax)) {
  if (sum(is.na(Listmax[[y]]$Maximal)) == length(Listmax[[y]]$Maximal)) {
    #skip this because ALL spare are "NA" 
    cat(y) 
    cat("Is missing all data")
    resultsmax <- rbind(resultsmax,c("NA", "NA", "NA", "NA"))
  } else {
    model<- nplr(x=Listbasal[[y]]$Concentration, y=Listbasal[[y]]$Maximal, useLog=FALSE, npars = 5)
    ID <- Listbasal[[y]]$Biological.replicate.number
    I <- model@inflPoint$x
    bA <- model@pars$bottom
    tA <- model@pars$top
    AUC <- model@AUC$Simpson
    resultsmax <- rbind(resultsmax,c(ID, I, bA, tA, AUC))
  }
}

resultsmax <-  resultsmax[c(8:12)]

x <- c("Biological.replicate.number", "I", "bA", "tA", "AUC")
colnames(resultsmax) = x

idv <- data[c(1:3,5)]
idv <-idv[!duplicated(idv), ]

resultsmax2 <- merge (idv, resultsmax, by=c("Biological.replicate.number"))
resultsmax2$AUC <- as.numeric(resultsmax2$AUC)

```

### 5.3.2. Model selection
```{r}
#Defining alternative models
max.null <- lm(AUC ~ 1, data=resultsmax2)
max.fit.1 <- lm(AUC ~ 1 + Drainage, data=resultsmax2)
max.fit.2 <- lm(AUC ~ 1 + Population, data=resultsmax2)
max.fit.3 <- lm(AUC ~ 1 + Drainage+Population, data=resultsmax2)
max.fit.4 <- lm(AUC ~ 1 + Drainage*Population, data=resultsmax2)

#Comparing alternative models
AICctab(max.null, max.fit.1, max.fit.2, max.fit.3, max.fit.4, base =T, weights = T)
```

Model 4 is the only model with dAICc < 2.

### 5.3.3. Assessment of best model (max.fit.4)
```{r}
Anova(max.fit.4, type = "III")
```


### 5.3.4. Visualization
```{r}
p3 <- ggplot(resultsmax2, aes(x=Drainage, y=AUC, fill=Population)) + 
      geom_boxplot() + 
      theme_classic() +
      scale_fill_manual(values=c("#5DA5DA", "#DECF3F")) + 
      theme(legend.position="none")+
      ggtitle("Mitochondrial function")
p3
```


## 5.4. Spare respiration
### 5.4.1. Drug response analysis
```{r warning=FALSE}
Listspare <- split(data, data$Biological.replicate.number)
resultsspare <- data.frame(matrix(ncol = 4, nrow = 0))

for (y in names(Listspare)) {
  if (sum(is.na(Listspare[[y]]$Spare)) == length(Listspare[[y]]$Spare)) {
    #skip this because ALL spare are "NA" 
    cat(y) 
    cat("Is missing all data")
    resultsspare <- rbind(resultsspare,c("NA", "NA", "NA", "NA"))
  } else {
    model<- nplr(x=Listspare[[y]]$Concentration, y=Listspare[[y]]$Spare, useLog=FALSE, npars = 5)
    ID <- Listspare[[y]]$Biological.replicate.number
    I <- model@inflPoint$x
    bA <- model@pars$bottom
    tA <- model@pars$top
    AUC <- model@AUC$Simpson
    resultsspare <- rbind(resultsspare,c(ID, I, bA, tA, AUC))
  }
}

resultsspare <-  resultsspare[c(8:12)]

x <- c("Biological.replicate.number", "I", "bA", "tA", "AUC")
colnames(resultsspare) = x

idv <- data[c(1:3,5)]
idv <-idv[!duplicated(idv), ]

resultsspare2 <- merge (idv, resultsspare, by=c("Biological.replicate.number"))

```

### 5.4.2. Model selection
```{r}
#Defining alternative models
spare.null <- lm(AUC ~ 1, data=resultsspare2)
spare.fit.1 <- lm(AUC ~ 1 + Drainage, data=resultsspare2)
spare.fit.2 <- lm(AUC ~ 1 + Population, data=resultsspare2)
spare.fit.3 <- lm(AUC ~ 1 + Drainage+Population, data=resultsspare2)
spare.fit.4 <- lm(AUC ~ 1 + Drainage*Population, data=resultsspare2)

#Comparing alternative models
AICctab(spare.null, spare.fit.1, spare.fit.2, spare.fit.3, spare.fit.4, base =T, weights = T)
```

Model 4 is the only model with dAICc < 2.

### 5.4.3. Assessment of best model (spare.fit.4)
```{r}
Anova(spare.fit.4, type = "III")
```


### 5.4.4. Visualization
```{r}
p1 <- ggplot(resultsspare2, aes(x=Drainage, y=AUC, fill=Population)) + 
      geom_boxplot() + 
      theme_classic() +
      scale_fill_manual(values=c("#5DA5DA", "#DECF3F")) + 
      theme(legend.position="none")+
      ggtitle("Mitochondrial function")
p1
```

## 5.5. Visualization of response curves
### 5.5.1. Basal respiration
```{r message=FALSE, warning=FALSE}
tacns<-data[which(data$ID == 'TacNS'),]
tacs<-data[which(data$ID == 'TacS'),]
puyns<-data[which(data$ID == 'PuyNS'),]
puys<-data[which(data$ID == 'PuyS'),]
pichns<-data[which(data$ID == 'PichNS'),]
pichs<-data[which(data$ID == 'PichS'),]

Basaltacns <- nplr(x=tacns$Concentration, y=tacns$Basal, useLog=FALSE)
Basaltacs <- nplr(x=tacs$Concentration, y=tacs$Basal, useLog=FALSE)
Basalpuyns <- nplr(x=puyns$Concentration, y=puyns$Basal, useLog=FALSE)
Basalpuys <- nplr(x=puys$Concentration, y=puys$Basal, useLog=FALSE)
Basalpichns <- nplr(x=pichns$Concentration, y=pichns$Basal, useLog=FALSE)
Basalpichs <- nplr(x=pichs$Concentration, y=pichs$Basal, useLog=FALSE)


x1 <- data$Concentration; y1 <- data$Basal
x2 <- getXcurve(Basaltacns); y2 <- getYcurve(Basaltacns)
x3 <- getXcurve(Basaltacs); y3 <- getYcurve(Basaltacs)
x4 <- getXcurve(Basalpuyns); y4 <- getYcurve(Basalpuyns)
x5 <- getXcurve(Basalpuys); y5 <- getYcurve(Basalpuys)
x6 <- getXcurve(Basalpichns); y6 <- getYcurve(Basalpichns)
x7 <- getXcurve(Basalpichs); y7 <- getYcurve(Basalpichs)

data1<-data.frame(x1,y1)
data2<-data.frame(x2,y2)
data3<-data.frame(x3,y3)
data4<-data.frame(x4,y4)
data5<-data.frame(x5,y5)
data6<-data.frame(x6,y6)
data7<-data.frame(x7,y7)

data1tacns<-data.frame(tacns$Concentration,tacns$Basal)
data1tacs<-data.frame(tacs$Concentration,tacs$Basal)
data2tacns<-data.frame(x2,y2)
data3tacs<-data.frame(x3,y3)
PlotBasalTac <- ggplot(data1tacns,aes(tacns$Concentration,tacns$Basal)) + geom_point(color="#5DA5DA") +
  geom_point(data=data1tacs,aes(tacs$Concentration,tacs$Basal), color="#DECF3F") +
  ylab("Basal respiratory capacity") + xlab("H2S concentration") +  xlim(0, 100) + 
  geom_line(data=data2tacns,aes(x2,y2),color="#5DA5DA", linetype=1)+geom_line(data=data3tacs,aes(x3,y3),color="#DECF3F", linetype=1) + theme_classic()+
  ggtitle("Basal respiration: Tacotalpa")


dataPuyns<-data.frame(puyns$Concentration,puyns$Basal)
dataPuys<-data.frame(puys$Concentration,puys$Basal)
data4Puyns<-data.frame(x4,y4)
data5PuyS<-data.frame(x5,y5)
PlotBasalPuy <- ggplot(dataPuyns,aes(puyns$Concentration,puyns$Basal)) + geom_point(color="#5DA5DA") +
  geom_point(data=dataPuys,aes(puys$Concentration,puys$Basal), color="#DECF3F") +
  ylab("Basal respiratory capacity") + xlab("H2S concentration") +  xlim(0, 100) + 
  geom_line(data=data4Puyns,aes(x4,y4),color="#5DA5DA", linetype=1)+geom_line(data=data5PuyS,aes(x5,y5),color="#DECF3F", linetype=1) + theme_classic()+
  ggtitle("Basal respiration: Puyacatengo")


dataPichns<-data.frame(pichns$Concentration,pichns$Basal)
dataPichs<-data.frame(pichs$Concentration,pichs$Basal)
data6Pichns<-data.frame(x6,y6)
data7Pichs<-data.frame(x7,y7)
PlotBasalPich <- ggplot(dataPichns,aes(pichns$Concentration,pichns$Basal)) + geom_point(color="#5DA5DA") +
  geom_point(data=dataPichs,aes(pichs$Concentration,pichs$Basal), color="#DECF3F") +
  ylab("Basal respiratory capacity") + xlab("H2S concentration") +  xlim(0, 100) + 
  geom_line(data=data6Pichns,aes(x6,y6),color="#5DA5DA", linetype=1)+geom_line(data=data7Pichs,aes(x7,y7),color="#DECF3F", linetype=1) + theme_classic()+
  ggtitle("Basal respiration: Pichucalco")

multiplot(PlotBasalTac,PlotBasalPuy,PlotBasalPich, cols=2)
```

### 5.5.2. Maximal respiration
```{r message=FALSE, warning=FALSE}
tacns<-data[which(data$ID == 'TacNS'),]
tacs<-data[which(data$ID == 'TacS'),]
puyns<-data[which(data$ID == 'PuyNS'),]
puys<-data[which(data$ID == 'PuyS'),]
pichns<-data[which(data$ID == 'PichNS'),]
pichs<-data[which(data$ID == 'PichS'),]

Maximaltacns <- nplr(x=tacns$Concentration, y=tacns$Maximal, useLog=FALSE)
Maximaltacs <- nplr(x=tacs$Concentration, y=tacs$Maximal, useLog=FALSE)
Maximalpuyns <- nplr(x=puyns$Concentration, y=puyns$Maximal, useLog=FALSE)
Maximalpuys <- nplr(x=puys$Concentration, y=puys$Maximal, useLog=FALSE)
Maximalpichns <- nplr(x=pichns$Concentration, y=pichns$Maximal, useLog=FALSE)
Maximalpichs <- nplr(x=pichs$Concentration, y=pichs$Maximal, useLog=FALSE)


x1 <- data$Concentration; y1 <- data$Maximal
x2 <- getXcurve(Maximaltacns); y2 <- getYcurve(Maximaltacns)
x3 <- getXcurve(Maximaltacs); y3 <- getYcurve(Maximaltacs)
x4 <- getXcurve(Maximalpuyns); y4 <- getYcurve(Maximalpuyns)
x5 <- getXcurve(Maximalpuys); y5 <- getYcurve(Maximalpuys)
x6 <- getXcurve(Maximalpichns); y6 <- getYcurve(Maximalpichns)
x7 <- getXcurve(Maximalpichs); y7 <- getYcurve(Maximalpichs)

data1<-data.frame(x1,y1)
data2<-data.frame(x2,y2)
data3<-data.frame(x3,y3)
data4<-data.frame(x4,y4)
data5<-data.frame(x5,y5)
data6<-data.frame(x6,y6)
data7<-data.frame(x7,y7)

data1tacns<-data.frame(tacns$Concentration,tacns$Maximal)
data1tacs<-data.frame(tacs$Concentration,tacs$Maximal)
data2tacns<-data.frame(x2,y2)
data3tacs<-data.frame(x3,y3)
PlotMaximalTac <- ggplot(data1tacns,aes(tacns$Concentration,tacns$Maximal)) + geom_point(color="#5DA5DA") +
  geom_point(data=data1tacs,aes(tacs$Concentration,tacs$Maximal), color="#DECF3F") +
  ylab("Maximal respiratory capacity") + xlab("H2S concentration") +  xlim(0, 100) + 
  geom_line(data=data2tacns,aes(x2,y2),color="#5DA5DA", linetype=1)+geom_line(data=data3tacs,aes(x3,y3),color="#DECF3F", linetype=1) + theme_classic()+
  ggtitle("Maximal repiration: Tacotalpa")


dataPuyns<-data.frame(puyns$Concentration,puyns$Maximal)
dataPuys<-data.frame(puys$Concentration,puys$Maximal)
data4Puyns<-data.frame(x4,y4)
data5PuyS<-data.frame(x5,y5)
PlotMaximalPuy <- ggplot(dataPuyns,aes(puyns$Concentration,puyns$Maximal)) + geom_point(color="#5DA5DA") +
  geom_point(data=dataPuys,aes(puys$Concentration,puys$Maximal), color="#DECF3F") +
  ylab("Maximal respiratory capacity") + xlab("H2S concentration") +  xlim(0, 100) + 
  geom_line(data=data4Puyns,aes(x4,y4),color="#5DA5DA", linetype=1)+geom_line(data=data5PuyS,aes(x5,y5),color="#DECF3F", linetype=1) + theme_classic()+
  ggtitle("Maximal repiration: Puyacatengo")


dataPichns<-data.frame(pichns$Concentration,pichns$Maximal)
dataPichs<-data.frame(pichs$Concentration,pichs$Maximal)
data6Pichns<-data.frame(x6,y6)
data7Pichs<-data.frame(x7,y7)
PlotMaximalPich <- ggplot(dataPichns,aes(pichns$Concentration,pichns$Maximal)) + geom_point(color="#5DA5DA") +
  geom_point(data=dataPichs,aes(pichs$Concentration,pichs$Maximal), color="#DECF3F") +
  ylab("Maximal respiratory capacity") + xlab("H2S concentration") +  xlim(0, 100) + 
  geom_line(data=data6Pichns,aes(x6,y6),color="#5DA5DA", linetype=1)+geom_line(data=data7Pichs,aes(x7,y7),color="#DECF3F", linetype=1) + theme_classic()+
  ggtitle("Maximal repiration: Pichucalco")


```

### 5.5.3. Spare respiration
```{r message=FALSE, warning=FALSE}
tacns<-data[which(data$ID == 'TacNS'),]
tacs<-data[which(data$ID == 'TacS'),]
puyns<-data[which(data$ID == 'PuyNS'),]
puys<-data[which(data$ID == 'PuyS'),]
pichns<-data[which(data$ID == 'PichNS'),]
pichs<-data[which(data$ID == 'PichS'),]

Sparetacns <- nplr(x=tacns$Concentration, y=tacns$Spare, useLog=FALSE)
Sparetacs <- nplr(x=tacs$Concentration, y=tacs$Spare, useLog=FALSE)
Sparepuyns <- nplr(x=puyns$Concentration, y=puyns$Spare, useLog=FALSE)
Sparepuys <- nplr(x=puys$Concentration, y=puys$Spare, useLog=FALSE)
Sparepichns <- nplr(x=pichns$Concentration, y=pichns$Spare, useLog=FALSE)
Sparepichs <- nplr(x=pichs$Concentration, y=pichs$Spare, useLog=FALSE)


x1 <- data$Concentration; y1 <- data$Spare
x2 <- getXcurve(Sparetacns); y2 <- getYcurve(Sparetacns)
x3 <- getXcurve(Sparetacs); y3 <- getYcurve(Sparetacs)
x4 <- getXcurve(Sparepuyns); y4 <- getYcurve(Sparepuyns)
x5 <- getXcurve(Sparepuys); y5 <- getYcurve(Sparepuys)
x6 <- getXcurve(Sparepichns); y6 <- getYcurve(Sparepichns)
x7 <- getXcurve(Sparepichs); y7 <- getYcurve(Sparepichs)

data1<-data.frame(x1,y1)
data2<-data.frame(x2,y2)
data3<-data.frame(x3,y3)
data4<-data.frame(x4,y4)
data5<-data.frame(x5,y5)
data6<-data.frame(x6,y6)
data7<-data.frame(x7,y7)

data1tacns<-data.frame(tacns$Concentration,tacns$Spare)
data1tacs<-data.frame(tacs$Concentration,tacs$Spare)
data2tacns<-data.frame(x2,y2)
data3tacs<-data.frame(x3,y3)
PlotSpareTac <- ggplot(data1tacns,aes(tacns$Concentration,tacns$Spare)) + geom_point(color="#5DA5DA") +
  geom_point(data=data1tacs,aes(tacs$Concentration,tacs$Spare), color="#DECF3F") +
  ylab("Spare respiratory capacity") + xlab("H2S concentration") +  xlim(0, 100) + 
  geom_line(data=data2tacns,aes(x2,y2),color="#5DA5DA", linetype=1)+geom_line(data=data3tacs,aes(x3,y3),color="#DECF3F", linetype=1) + theme_classic()+
  ggtitle("Tacotalpa")

dataPuyns<-data.frame(puyns$Concentration,puyns$Spare)
dataPuys<-data.frame(puys$Concentration,puys$Spare)
data4Puyns<-data.frame(x4,y4)
data5PuyS<-data.frame(x5,y5)
PlotSparePuy <- ggplot(dataPuyns,aes(puyns$Concentration,puyns$Spare)) + geom_point(color="#5DA5DA") +
  geom_point(data=dataPuys,aes(puys$Concentration,puys$Spare), color="#DECF3F") +
  ylab("Spare respiratory capacity") + xlab("H2S concentration") +  xlim(0, 100) + 
  geom_line(data=data4Puyns,aes(x4,y4),color="#5DA5DA", linetype=1)+geom_line(data=data5PuyS,aes(x5,y5),color="#DECF3F", linetype=1) + theme_classic()+
  ggtitle("Puyacatengo")

dataPichns<-data.frame(pichns$Concentration,pichns$Spare)
dataPichs<-data.frame(pichs$Concentration,pichs$Spare)
data6Pichns<-data.frame(x6,y6)
data7Pichs<-data.frame(x7,y7)
PlotSparePich <- ggplot(dataPichns,aes(pichns$Concentration,pichns$Spare)) + geom_point(color="#5DA5DA") +
  geom_point(data=dataPichs,aes(pichs$Concentration,pichs$Spare), color="#DECF3F") +
  ylab("Spare respiratory capacity") + xlab("H2S concentration") +  xlim(0, 100) + 
  geom_line(data=data6Pichns,aes(x6,y6),color="#5DA5DA", linetype=1)+geom_line(data=data7Pichs,aes(x7,y7),color="#DECF3F", linetype=1) + theme_classic()+
  ggtitle("Pichucalco")

multiplot(PlotSpareTac,PlotSparePuy,PlotSparePich, cols=2)
```

